Foreign Exchange Speculation: An Event Study

### 2018-01-19 MDPI/MDPI_template/FinStudies.tex
Updaed some parts of the paper.

\begin{document}
\section{Introduction}
\added{Speculation can be stabilising or destabilising.} If speculation is based on information it is a stabilising force, providing liquidity and helping to ensure that markets swiftly find equilibrium. \citet{KeynesHedge} and \citet{HicksHedge} \deleted{for example} emphasise the role that speculation plays in facilitating financial market transactions \added{by providing liquidity that allows hedgers and other market participants to swiftly find counterparties without the need for large prices concessions. In this version, speculators} \deleted{Speculators} offer a service for a fee that is determined by the return on their activity.  \replaced{\citet{FriedmanPositive} argued that even where there is a mixture of infomed and unnformed speculators, the informed woudl tend to buy when prices were below intrinsic value and sell when above, making profits, stabilising the market and driving the loss-making uninformed speculators out of business.}{While speculators may be trading on information or noise, informed speculators will tend to drive out the uninformed noise-traders according to \citet{FriedmanPositive}.} \deleted{However, the later} \citet[p. 101]{Keynes1936} \added{also had a later, more negative view of speculation.  Here he} regarded it as a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd''\added{. Uninformed speculators may now dominate} and \citet{Delong1990noise} provide a model \deleted{of cases} where speculative noise \replaced{constrains}{provides a constraint on} informed traders \added{from} benefiting from their knowledge. Now speculation is an uninformed and destabilising force.  \added{We have therefore two concepts of speculation: one that is random and disruptive and one that is informed and beneicial in its provison of liqidity.

The debate about the relative merit of these two concepts of speculation continues. There has been particular focus on commodities markets and foreign exchange markets.  \citet{Jacksspec} documents a long history of attacks on speculation following price volatility.} This has been particularly evident in commodities and foreign exchange markets.  There has been much discussion over the role that speculation played in the boom and bust of commodities prices in the period between 2006 and 2007.  \citet{TangSpec} suggest that this disruption was exacerbated by newly estabilished commodity indices that encoraged speculation.

There have also been investigations of the link between speclulation or noise trading and price misalignments or volatility across a range of other asset marketsA.  \citet{Verma} examine the link between noise trading and equity markets; \citet{Hongjun} asks whether speculation in aggregate is just random noise lacking influence on prices.  Howevever, foreign exchange has been a particular focus as a consequence of its liquidity, volatility and the way that speculative attacks appear to have infringed on government soverignty.  See \citet{Dornbusch1988} in geneal and \citet{Eichengreen1988} for discussion of the speculative attacks on the European exchange rate system.  \citet{Eichengreen1994} use a set of fundamentals to show that speculative attacks drove exchange rates away from their fundamental value. However, others have made the case that speculative is a key part of the forign exchange market, providing liquidity and contribuing to stability.  See \citet{Mayer1985} and \citet{McKinnon1986}.

There is no consensus and the the debate enters policy circles with the suggestion that a tax on financial transactions could reduce speculation and thereby limit misalignment and volatility. \citet[pp.158]{TobinTax} and \citet{Tobin1988a} say that such a tax would "throw some sand in the well-greased wheels." of the foreign exchange market. At face value the tax has the advantage of improving market efficiency and raising funds for other welfare-enhancing acitvity.  However, this is only the case if speculation is uninformed and destabilising.  If it is informed and contributes to stability the tax will come at a cost.

@@

The intenisty of speculation is measured in two ways: speculative sentiment and speculative positions.  Speculative sentiment is identified with the use of option risk-reversal skew.  As these become more extreme it signals that expectations of future value in the foreign exchange options market have diverged significantly from the appropraite forward rate.  The Weight of speculative positions is identified with US regulatory data of the psotions held by type of participant in the futures market.  Net long and net short are open positions held by spculators relative to overall activit in the market. See Section \ref{secref:measure} for full data details.}

@@

\section{Informed and uninformed speculation}
Speculation plays an important part in several areas of financial economics.  However, there is no clear, unambiguous theory of speculation.  Speculation is frequently associated with the term trading and the provision of liquidity, but trading is broader as it encompasses financial investment while liquidity provision is really market-making. Speculation and trading can be categorised as being informed or uninformed. Those trading without information are frequently called \emph{noise-traders} or \emph{liquidity traders}.  However, the terms are not fixed and  \citet[p. 1]{GortonNoise} categorise noise-traders as all those trading in markets for ``non-information-based reasons''.  See \citet{Ramiah201589} for a recent review of the noise-trader literature.

@@

\added{This study is about short-term movements in foreign exchange prices.  The event windows are between 1 week and 4 weeks in length. While the interpretation of economic fundamentals can drive prices, market posotions and liquidity trades will also be important.  Even at longer horizons it is often very difficult to connect exchange rate movements to specific events. \citet{Meese1983Empirical} find that forecasts using exchange rate models cannot beat a random walk while \citet{ChinnModel} updated the study to find very similar results. 
.  
The foreign exchange market is primarily a dealer-orientated market.  It is largely consistent with the theortical microstructure models that have been presented by the likes of \citet{Kyle1985Continuous} and \citet{glosten1985bid}. The interaction of informed and uninformed traders drives the price-discovery process: if the uninformed traders are random, the market-maker earns the bid-ask spread; if informed traders arrive they drive the price towards equilibrium.}

If the movement of the price of foreign exchange towards equilibrium, \emph{price discovery} is facilitated by order flow from informed traders (as has been asserted theoetically by \citet{Glosten1985Bid} and \citet{Kyle1985Continuous} while being demonstrted empirically by \citet{Lyons1995Microstructure} and \citet{Evans2002Order} and \citet{rime2010exchange}, speculative sentiment and positions would be part of the price discovery process if informed and would disript this process if not. Therefore,}if speculators are informed their activity drives exchange rates towards equilibrium and prices should follow a random walk after these extremes of speculative sentiment or position; if speculators are uninformed and their activity can be regarded as noise, the most extreme speculative sentiment and the time when speculators have the greatest weight in the market should correspond with the greatest deviation of prices from fundamental value, when subsequent price reversals are most likely to take place.

@@

It is common practice to back market expectations out of information drawn from option prices.  See \citet{Malickoption} and \citet{Pochin} for the general approach that combines the implied volatility, risk-reversal and strangles to infer a mixed distrubtion that can be inferreed as the risk-neutral probabiolity density function for a particular asset. See \citet{Gaati} an application on the Yen-dollar exchange rate where expectations are affected by central bank intervention. Using the risk-reversal is a simplified version of that where the skew is used to infer positive and expectations relative to the appropriate forward rate.  See ??? for previous uses of this data.}

@@

Recording speculative activity in an over-the-counter market like foreign exchange is extremely difficult.  However, there are some exchange-traded currency derivative markets in the US, and participants in these markets are required to report their positions to the US regulators.  The Commodity Futures Trading Commission (CFTC) collect weekly information about the open positions held by private entities in the US derivative markets.   A sub-set of this information is released to the public each week as the \emph{Commitment of Traders Report} (CoT).\footnote{The \citet{cot} require traders to categorise themselves as being either commercial (C) or non-commercial (NC).  Commercial traders must have some underlying business interest in the security, commodity or instrument that they are trading.  These could be seen as natural hedgers.  Non-commercial accounts are generally considered to be speculators.  See \citet{FuturesSanders} and \citet{FuturesWang} for examples of previous use of this data in this fashion.

The data used run from September 30 1998 when the data started to be released on a weekly basis and continue up to December 31 2008.  The Euro data runs from March 3 1998 to December 31 2008.  There are two gaps in the Swiss Franc data for September 14 2004 and September 21 2004.  The absence of these data seems to be a result of problems with the CFTC database.  The contracts are for EUR 100,000; GBP 62,500; JPY 12,500,000; CHF 100,000 and CAD 100,000.}

An event study will analyse the performance of security of asset prices around an event.  In this case the event is the extreme of speculative sentiment or extreme speculative activity.  See \citet{Dolly1933} for the original version of the event study method and \citet{FamaFisherJensenRoll} for an overview of the method used in this study.

@@

The results are not a function of the design of the event study.  The event window and the quantiles that are chosen to measure the extreme can be changed.  Alternative measures produced very similar results. Alternative quantiles from 1\% and 99\% to 20\% and 80\% have been assessed; Figures \ref{fig:ES1}, \ref{fig:ES2}, \ref{fig:ES3} and \ref{fig:ES4} have much wider windows and do not find any alternative to the view that extreme speculation is followed by a random walk.

It is encouraging that two very different measures of speculative activity produce very similar results and that the results hold over different time frames: one week for the option data and one week for the regulatory position data.  It is less clear whether the results would be reproduced across markets for other financial assets. \added{The foreign exchange market has a particular microstructure that is dominated by over-the-counter transactions in the spot market and this may influence the results.  Further reseach might look at risk-reversals in financial markets that are traded on electronic exchanges to see if these results are replicated.  The data on speculative positions are from the excahnge traded futures market.} \deleted{The results do not rule out uninformed speculation.  The Friedman effect from the Noise-trader model, whereby the informed speculators take advantage of the space created by price pressure from the uniformed, depends on there being \emph{noise-trader risk} or some limits to arbitrage.  The effect is not evident in this study.}  However, the foreign exchange market is a particularly large and liquid market, other asset classes may have alternative institutional features that mean a different relationship or balance between the informed and uninformed and therefore different results.

\added{It is possible to dispute the link between risk reversal and market sentiment. It is not only the direct change in expectations about the future that affect  risk-reversals. The weight of positions from hedging activity could be influential. Therefore future research might also investigate the link between these figures and other measures of short-term sentiment if they exist.}
\deleted{This is important because there is no unambiguous view of speculative activity and because speculation is an important issues in a number of policy debates.  Most notably, the \emph{Tobin Tax} would put a charge against financial transactions, particularly in foreign exchange.  Part of the argument depends on speculation being uninformed as the reduced activity that is caused by the tax would, it is argued, limit volatility and allow more long-term fundamental evaluations to become prominent.  However, if speculation is informed and part of the price discovery process, this tax may have the opposite effect to what is envisaged.  These results suggest that it could reduce liquidity and increase volatility.}

>>>>

\begin{document}
\section{Introduction}
\added{Speculation can be viewed as stabilising or destabilising.  If speculation is informed, it is a stabilising force, providing liquidity and helping to ensure that markets swiftly find equilibrium.  \citet{KeynesHedge} and \citet{HicksHedge} emphasise the role that speculation plays in facilitating financial market transactions by providing liquidity that allows hedgers and other market participants to swiftly find counterparties without the need for large price concessions.  In this version, speculators offer a service for a fee that is determined by the return on their activity.  \citet{FriedmanPositive} argued that even whew there is a mixture of informed and uninformed speculators, the informed would tend to buy when prices were below intrinsic value and sell when above, making profits, limiting volatility and driving the loss-making uninformed speculators out of business.  However, \citet[p. 101]{Keynes1936} also had a later, more negative view of speculations.  Here he regarded it as a myopic, sentient-driven activity, dominated by the desire to ``beat the gun`` or ``outwit the crowd.  Uninformed speculators may now dominate and \citet{Delong1990noise} provide a model where speculative noise constrains informed traded from benefiting from their knowledge.  Now speculation is an uninformed and destabilising force.  We have therefore two concepts of speculation:  one that is random and disruptive and one that is informed and beneficial.

%\added{Speculation can be viewed as stabilising or destabilising.} If speculation is based on information it is a stabilising force, providing liquidity and helping to ensure that markets swiftly find equilibrium. \citet{KeynesHedge} and \citet{HicksHedge} \deleted{for example} emphasise the role that speculation plays in facilitating financial market transactions \added{by providing liquidity that allows hedgers and other market participants to swiftly find counterparties without the need for large prices concessions. In this version, speculators} \deleted{Speculators} offer a service for a fee that is determined by the return on their activity.  \added{\citet{FriedmanPositive} argued that even where there is a mixture of informed and uninformed speculators, the informed would tend to buy when prices were below intrinsic value and sell when above, making profits, limiting volatility and driving the loss-making uninformed speculators out of business.}\deleted{While speculators may be trading on information or noise, informed speculators will tend to drive out the uninformed noise-traders according to \citet{FriedmanPositive}.} However, \deleted{the later} \citet[p. 101]{Keynes1936} \added{also had a later, more negative view of speculation.  Here he} regarded it as a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd''\added{. Uninformed speculators may now dominate} and \citet{Delong1990noise} provide a model \deleted{of cases} where speculative noise \replaced{constrains}{provides a constraint on} informed traders \added{from} benefiting from their knowledge. Now speculation is an uninformed and destabilising force.  \added{We have therefore two concepts of speculation: one that is random and disruptive and one that is informed and beneficial in its proviso of liquidity.

The debate about the relative merit of these two concepts of speculation continues. There has been particular focus on commodities markets and foreign exchange markets.  \citet{Jacksspec} documents a long history of attacks on speculation following price volatility. This has been particularly evident in commodities and foreign exchange markets.  There has been much discussion over the role that speculation played in the boom and bust of commodities prices in the period between 2006 and 2007.  \citet{TangSpec} suggest that this disruption was exacerbated by newly established commodity indices that encouraged speculation.

There have also been investigations of the link between speculation or noise trading and price misalignments or volatility across a range of other asset markets.  \citet{Verma} examine the link between noise trading and equity markets; \citet{Hongjun} argues that speculation is not random and influential in aggregation but that behavioural biases will cause systematic deviations from intrinsic value. Foreign exchange has been a particular focus as a consequence of its liquidity, volatility and the way that speculative attacks appear to have infringed on government sovereignty.  See \citet{Dornbusch1988} in general and \citet{Eichengreen1988} for discussion of the speculative attacks on the European exchange rate system.  \citet{Eichengreen1994} use a set of fundamentals to show that speculative attacks drove exchange rates away from their fundamental value. However, others have made the case that speculative is a key part of the foreign exchange market, providing liquidity and contributing to stability.  See \citet{Mayer1985} and \citet{McKinnon1986}.

There is no consensus and the the debate enters policy circles with the suggestion that a tax on financial transactions could reduce speculation and thereby limit misalignment and volatility. \citet[pp.158]{TobinTax} and \citet{Tobin1988a} say that such a tax would "throw some sand in the well-greased wheels." of the foreign exchange market. At face value the tax has the advantage of improving market efficiency and raising funds for other welfare-enhancing activity.  However, this is only the case if speculation is uninformed and destabilising.  If it is informed and contributes to stability the tax will come at a cost.}

@@

The intensity of speculation is measured in two ways: speculative sentiment and speculative positions.  Speculative sentiment is identified with the use of option risk-reversal skew.  As these become more extreme it signals that expectations of future value in the foreign exchange options market have diverged significantly from the appropriate forward rate.  The Weight of speculative positions is identified with US regulatory data of the positions held by type of participant in the futures market.  Net long and net short are open positions held by speculators relative to overall activity in the market. See Section \ref{secref:measure} for full data details.}

@@

\section{Informed and uninformed speculation}
Speculation plays an important part in several areas of financial economics.  However, there is no clear, unambiguous theory of speculation.  Speculation is frequently associated with the term trading and the provision of liquidity, but trading is broader as it encompasses financial investment while liquidity provision is really market-making. Speculation and trading can be categorised as being informed or uninformed. Those trading without information are frequently called \emph{noise-traders} or \emph{liquidity traders}.  \added{The first implies some random quality that flow from the lack of information.  However, the psychologists find that the cognitive short-cuts or \emph{heuristics} that are used to make decisions under uncertainty tend to have biases \citet{Kahneman1979Prospect} and numerous studies purport to find these biases in financial asset prices.  For example, \citet{DeBondtOver} find evidence that \emph{representativeness} causes stock prices to overshoot and \citet{Coval2005} identifies evidence of behavioural biases among Chicago Board of Trade proprietary traders.  Liquidity trades are generally those carrying out transactions for reasons other than value.  This can be passive investment funds buying stocks as money is drawn from investors or hedging activity that does not depend on price.    The terms are not fixed and  \citet[p. 1]{GortonNoise} categorise noise-traders as all those trading in markets for ``non-information-based reasons''.  See \citet{Ramiah201589} for a recent review of the noise-trader literature.

@@

\added{The foreign exchange market is primarily a dealer-orientated market.  It is largely consistent with the theoretical microstructure models that have been presented by the likes of \citet{Kyle1985Continuous} and \citet{glosten1985bid}. The interaction of informed and uninformed traders drives the price-discovery process: if the uninformed traders are random, the market-maker earns the bid-ask spread; if informed traders arrive they drive the price towards equilibrium.  This study is about short-term movements in foreign exchange prices.  The event windows are between 1 week and 4 weeks in length. While the interpretation of economic fundamentals can drive prices, market positions and liquidity trades will also be important.  Even at longer horizons it is often very difficult to connect exchange rate movements to specific events. \citet{Meese1983Empirical} find that forecasts using exchange rate models cannot beat a random walk while \citet{ChinnModel} updated the study to find very similar results. \citet{Lyons1995Microstructure}, \citet{Evans2002Order} and \citet{rime2010exchange} show that order flow can explain exchange rate movements much more effectively than fundamentals. The initiating or forcing orders drive the price.  Therefore, deliberate speculative should drive the price.  Speculative sentiment changes and speculative positions changes would be part of the price discovery process if informed and would disrupt this process if not. Therefore,if speculators are informed their activity drives exchange rates towards equilibrium and prices should follow a random walk after these extremes of speculative sentiment or position; if speculators are uninformed and their activity can be regarded as noise, the most extreme speculative sentiment and the time when speculators have the greatest weight in the market should correspond with the greatest deviation of prices from fundamental value, when subsequent price reversals are most likely to take place.  }

@@

It is common practice to back market expectations out of information drawn from option prices.  See \citet{Malickoption} and \citet{Pochin} for the general approach that combines the implied volatility, risk-reversal and strangles to infer a mixed distribution that can be inferred as the risk-neutral probability density function for a particular asset. See \citet{Gaati} an application on the Yen-dollar exchange rate where expectations are affected by central bank intervention. Using the risk-reversal is a simplified version of that where the skew is used to infer positive and expectations relative to the appropriate forward rate.  See \citet{Eitrheim} and \citet{ECBRR} for previous uses of this data.}

@@

Recording speculative activity in an over-the-counter market like foreign exchange is extremely difficult.  However, there are some exchange-traded currency derivative markets in the US, and participants in these markets are required to report their positions to the US regulators.  The Commodity Futures Trading Commission (CFTC) collect weekly information about the open positions held by private entities in the US derivative markets.   A sub-set of this information is released to the public each week as the \emph{Commitment of Traders Report} (CoT).The \citet{cot} require traders to categorise themselves as being either commercial (C) or non-commercial (NC).  Commercial traders must have some underlying business interest in the security, commodity or instrument that they are trading.  These could be seen as natural hedgers.  Non-commercial accounts are generally considered to be speculators.  See \citet{FuturesSanders} and \citet{FuturesWang} for examples of previous use of this data in this fashion.    The data used run from September 30 1998 when the data started to be released on a weekly basis and continue up to December 31 2008.  The Euro data runs from March 3 1998 to December 31 2008.  There are two gaps in the Swiss Franc data for September 14 2004 and September 21 2004.  The absence of these data seems to be a result of problems with the CFTC database.  The contracts are for EUR 100,000; GBP 62,500; JPY 12,500,000; CHF 100,000 and CAD 100,000.  Two new series are created from the raw data.  These are labelled S1 and S2.  S1 measures net non-commercial positions relative to the total non-commercial positions and S2 measures non-commercial positions relative to open interest.

\begin{equation}
S1 = \frac{NCL - NCS}{NCL + NCS + NCSP}
\end{equation}

Where NCL are the non-commercial long positions (holding non-US currency); NCS and non-commercial short positions and NCSP and the non-commercial spreading positions (spread long and short between different contract maturities). This will measure within the speculative group how biased they are towards holding long or short positions.

\begin{equation}
S2 = \frac{NCL - NCS}{OI}
\end{equation}

Where NCL are the non-commercial long positions (holding non-US currency); OI is the open interest in the contract. This will measure how biased speculators are to holding long or short positions relative to the whole market.  As such S2 is the preferred measure as it picks up not only direction but also the prominence of speculators relative to other agents.

S2 is the preferred measure as it

\added{\subsection{The Event Study}
An event study will be used to identify what happens to foreign exchange prices around the time that speculative sentiment or speculative positions are extreme.  If speculation is uninformed when speculative sentiment or speculative positions are extremely bias to one direction, there should be the greatest divergence from fundamental value and therefore the greatest risk of reversal; if speculation is informed these extremes are part of the adjustment to a new equilibrium.  An event study will analyse the performance of security of asset prices around an event.  In this case the event is the extreme of speculative sentiment or extreme speculative activity.

\citet{Dolly1933} is credited with the original event study method while \citet{FamaFisherJensenRoll} developed the method to investigate the reaction of equity prices to news of a stock split. An event study will look at the evolution of asset prices in a window around an \emph{event}. One of the major challenges in this process is to disentangle the effect of the event from all the other information that is around at that time.  This problem is usually addressed in two ways: modelling the expected value of the asset and viewing deviations from the expected value as being influenced by the event; using a large sample that, on the condition that there are no confounding factors at that time, would tend to dilute the effect of other information. In this case, the expected value should be the forward rate but given that we are looking at very short time horizons and interest rates for these currencies are relatively low, it is reasonable to take the expected value as zero and to investigate positive or negative exchange rate return.  The samples in this case depend on the how the \emph{extreme} sentiment and positions are defined.  As is seen in Table \ref{tabref:RR1} taking the $5^{th}$ and $95^{th}$ percentile as the extreme for the risk-reversal skew will give around 100 samples for each exchange rate; Table \ref{tabref:SP1} shows that the $95^{th}$ percentile gives just less than 50 samples for the extreme positions. The results do not seem to be sensitive to the definition of extreme. }

@@

The results are not a function of the design of the event study.  The event window and the quantiles that are chosen to measure the extreme can be changed.  Alternative measures produced very similar results. Alternative quantiles from 1\% and 99\% to 20\% and 80\% have been assessed; Figures \ref{fig:ES5}, \ref{fig:ES2}, \ref{fig:ES3} and \ref{fig:ES4} have much wider windows and do not find any alternative to the view that extreme speculation is followed by a random walk.  
It is encouraging that two very different measures of speculative activity produce very similar results and that the results hold over different time frames: one week for the option data and one week for the regulatory position data.  It is less clear whether the results would be reproduced across markets for other financial assets.

\added{The foreign exchange market has a particular microstructure that is dominated by over-the-counter transactions in the spot market and this may influence the results.  Further research might look at risk-reversals in financial markets that are traded on electronic exchanges to see if these results can be replicated.  The data on speculative positions are from the exchange traded futures market.} \deleted{The results do not rule out uninformed speculation.  The Friedman effect from the Noise-trader model, whereby the informed speculators take advantage of the space created by price pressure from the uniformed, depends on there being \emph{noise-trader risk} or some limits to arbitrage.  The effect is not evident in this study.}  However, the foreign exchange market is a particularly large and liquid market, other asset classes may have alternative institutional features that mean a different relationship or balance between the informed and uninformed and therefore different results.

\added{It is possible to dispute the link between risk reversal and market sentiment. It is not only the direct change in expectations about the future that affect  risk-reversals. The weight of positions from hedging activity could be influential. Therefore future research might also investigate the link between these figures and other measures of short-term sentiment if they exist.}  However, a number of studies have found that exchange rates tend to co-move with survey expectations (see for example \citet{FrankelFroot1987} and \citet{Frankel1987Using}.

\deleted{This is important because there is no unambiguous view of speculative activity and because speculation is an important issues in a number of policy debates.  Most notably, the \emph{Tobin Tax} would put a charge against financial transactions, particularly in foreign exchange.  Part of the argument depends on speculation being uninformed as the reduced activity that is caused by the tax would, it is argued, limit volatility and allow more long-term fundamental evaluations to become prominent.  However, if speculation is informed and part of the price discovery process, this tax may have the opposite effect to what is envisaged.  These results suggest that it could reduce liquidity and increase volatility.}

It is a common refrain that speculation is destabilising and that it will drive prices away from equilibrium.  Testing this assertion is difficult because speculation is difficult to measure and equilibrium cannot be viewed.  However, if speculation is destabilising, when speculators have the most extreme views of the future and when they are most involved in the market should lead to the greatest divergence from equilibrium and the greatest risk that prices will reverse.  Speculation is measured in two ways:  intensity of sentiment and positions.  In each case, foreign exchange prices move with speculative sentiment and speculative positions.  this is consistent with the deliberate orders move prices.  This would be consistent with speculation being part of the process of price discovery.  However, in each case the extreme does not tell us anything about the future direction of the prices.

Caveats:  futures are small?  risk reversal does not measure expectations, foreign exchange is different,
